---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BIOS625HW)
library(datasets)
library(fastDummies)

data(mtcars)
data(iris)
data("ToothGrowth")
data("USArrests")
```
# Package work flow
We will provide an example using the **iris** dataset. The goal is to fit a linear regression model to study the association between Sepal length and\ 
Sepal width\ 
Petal length\ 
Petal.Width\ 
Species\ 
```{r}
#Looking at the iris dataset
head(iris)
```
First we fit the model using *lm_blog*\  


Here we will pass *Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width + Species* and *iris* to *lm_blog* as save the model object as *lr*\  

```{r}
lr_iris <- lm_blog(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width + Species,iris)
```

Next we pass *lr_iris* to *summary_blog* to generate the results\  

```{r}
summary_blog(lr_iris)

```
# Test cases
## SLR - Covariate is continous
```{r}
lr_tg <- lm_blog(len ~ dose,ToothGrowth)
summary_blog(lr_tg)

```

## SLR - Covariate is continous
```{r}
lr_tg <- lm_blog(len ~ supp,ToothGrowth)
summary_blog(lr_tg)
```


## MLR - Covariates are all continous
```{r}
lr_us <- lm_blog(Murder ~ Assault + UrbanPop + Rape,USArrests)
summary_blog(lr_us)

```

## MLR - Covariates are both continous and categorical
```{r}
lr_iris <- lm_blog(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width + Species,iris)
summary_blog(lr_iris)

```

## If NA is preset in the dataset

```{r}
x1<-sample(c(NA,5,2),20,replace=TRUE)
x2<-sample(c(NA,10,100),20,replace=TRUE)
df1<-data.frame(x1,x2)

lr_na <- lm_blog(x1 ~ x2,df1)
summary_blog(lr_na)
```

# Comparing lm_blog() with lm() from the stats library

```{r}
#Fitted model using lm()

lr_lm <- lm(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width + Species,iris)

```

Checking the coefficient estimates

```{r}
all.equal(as.numeric(lr_iris[[3]]),as.numeric(lr_lm$coefficients))

```

Checking the estimated fitted values

```{r}
all.equal(as.numeric(lr_iris[[4]]),as.numeric(lr_lm$fitted.values))

```

# Comparing summary_blog() with summary() from the base R
```{r}
#Between models fitted using lm_blog() and lm()
summary(lr_lm)
summary_blog(lr_iris)

```

```{r}
#Between the same model fitted using lm_blog()
summary(lr_lm)
summary_blog(lr_iris)

```
